\warning{2016-09-01}{更新就读年级}
I am currently a first-year undergraduate student at University of California,
San Diego, with a declared major in Linguistics, a planned second major in
Mathematics, and a planned minor in Political Science.

I am a citizen of the People’s Republic of China and a native speaker of
Mandarin Chinese. My second language is English, though I am not good at it:
my vocabulary, especially words related with everyday life, is limited; my
speaking ability is notoriously bad. I don’t know other languages.

Academic facts. I am interested in computational linguistics and programming
language theory. My motivation is my belief in \link{@strongAI}. I hope to
increase machine’s ability in processing and understanding human languages.
I also believe that more advanced programming tools are essential to complex
AI. Still, I do not plan a computer science major. Reasons include:
\@ulist
  \@item I have been programming for nearly a decade\refSideNote{@csExp} and has
    experience with some basic algorithms. I believe I can learn most CS stuff
    by myself.
  \@item Maximum unit limitation of UCSD. During my undergraduate life I can
    take up to sixty courses here. If I choose a CS major I won’t have too many
    chances taking courses in mathematics, political science, or other
    interesting subjects.
  \@item Lack of self-discipline. I may be able to teach myself machine learning
    since \link{@nlp} requires it. But what, other than inner desire for
    knowledge, can drive me to read classics or advanced mathematics?

\local{@strongAI}{\mkLink{strong artificial intelligence}{https://en.wikipedia.org/wiki/Artificial_general_intelligence}}
\local{@nlp}{\mkLink{natural language processing}{https://en.wikipedia.org/wiki/Natural_language_processing}}
\local{@csExp}{\mkSideNote{Not so much experience in real world projects though.
I am more inclined to little toys and prototypes.}}

As mentioned above, I am struggling to gain self-discipline. In face, one of the
motivation of building this site is to update my progress in certain projects.
In this way, I can gain an illusion of supervision—since the progress is open to
any visitors—and therefore boost my efficiency.

I am interested in interface design. Here, “interface” is in its broad sense:
the interface of your oven, the information layout of this website, etc. My main
interest still lies in \link{@GUI} though.

\local{@GUI}{\mkLink{graphical user interface}{https://en.wikipedia.org/wiki/Graphical_user_interface}}

I love everything about Star Wars. My favorite character is \link{@padme} from
\link{@naberrie}. The affection clearly has nothing to do with the charm of
\link{@natalie}. If including \link{@swlegend}, the one receiving my most
respect \link{@plagueis}.

\local{@padme}{\mkLink{the lovely girl}{http://starwars.wikia.com/wiki/Padmé_Amidala}}
\local{@naberrie}{\mkLink{House Naberrie}{http://starwars.wikia.com/wiki/House_Naberrie}}
\local{@natalie}{\mkLink{Mrs. Millepied}{https://en.wikipedia.org/wiki/Natalie_Portman}}
\local{@swlegend}{\mkLink{Legends}{http://starwars.wikia.com/wiki/Star_Wars_Legends}}
\local{@plagueis}{\mkLink{Hego Damask, aka. Plagueis the Wise}{http://starwars.wikia.com/wiki/Darth_Plagueis}}
